Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-03 Ben_Manuscripts/structure_paper/supplemental.tex
Beefing up supplemental info

@@

  \textbf{TODO} : These are things I am working on / need to do

  \begin{itemize}
  \item Initial configuration dependence
	\begin{itemize}
		\item Initial pore-to-pore spacing
		\item Initial pore radius
		\item I have simulations running to support the claims that
		these are not significant factors if chosen within reason. And
		I will define what is meant by 'within reason'.
	\end{itemize}
  \item Description of parameterization process
  \item Feel free to suggest anything else that might be useful
  \end{itemize}

@@

>>>>

  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Further details regarding monomer parameterization}
  \endgroup

  Monomers were parameterized according to the following procedure:
  %BJC: need references
  \begin{enumerate}
	\item Create monomer structure file with connectivity : We drew atomistic
        structures using MarvinSketch 17.13. We optimized the 3D geometry of
	the structure using the 'Clean in 3D' function of MarvinSketch 17.13. 
        We saved the structure as a .mol file, then converted it to .pdb
	format using Open Babel 2.4.1. 
	\item Assign GAFF atomtypes using \texttt{antechamber} : Using the .pdb
	structure file as input, we ran \texttt{antechamber} using the AM1-BCC charge
	model. The net charge on the monomer is input as -1 since the sodium ion will
	be kept as a separate residue. The output of \texttt{antechamber} is used to
	create Amber topology files with \texttt{LEaP}. A detailed tutorial can be
	accessed elsewhere (http://ambermd.org/tutorials/basic/tutorial4b/) 
	\item Create gromacs topologies from Amber output : \texttt{LEaP}
	outputs a .inpcrd and a .prmtop file which are Amber topologies. Using
	acpype.py, we convert the \texttt{LEaP} output into GROMACS .gro and .top
	files. 
  \end{enumerate}

@@

@@

  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Initial Configuration Dependence}
  \endgroup

  Any major dependence on initial configuration is addressed in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
  monomers per layer in the sandwiched configuration.

  There are three other parameters whose choice may influence the equilibrium
  structure: initial pore spacing, initial pore radius and initial distance
  between layers. Here we show the results of a sensitivity analysis performed
  on the three parameters. To reduce the size of the sensitivity analysis, we
  only tested systems built with 5 monomers per layer with layers stacked in 
  the parallel displaced configuration. All systems were equilibrated according
  to the dry equilibration procedure.

  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.

  \begin{enumerate}

	  \item \underline{Initial pore spacing}

	  We tested five different initial pore spacings, defined as the
	  distance between the central axis of each pore with all others. To reduce the
	  number of variables, we held the pore radius constant, at 5 \AA~and the
	  distance between layers at 3.7 \AA~since those were the values used in our
	  optimal system in the main text. If the initial pore spacing is chosen to be
	  too small, pore columns abruptly repel each other as soon as they are able to
	  overcome the restraining potential present as part of the dry equilibration
	  procedure. We avoided using systems that exhibit this behavior since the
	  behavior increases the chances of a system to become kinetically trapped in an
	  undesired metastable free energy basin.

	  \begin{enumerate}

	  	\item 39 \AA~: A pore spacing of 39 \AA~is used in order to have a test system
		started with a spacing below the experimental value. As soon as the restraining
		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).

		\item 41 \AA~: A pore spacing of 41 \AA~is chosen since it closely matches the
		experimental pore spacing.  Again, we observe abrupt repulsion of columns once
		the restraining potential is switched to 56 KJ mol$^{-1}$ nm$^{-2}$
		(Figure~\ref{fig:p2p_41}).

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger than the
		experimental value. We observe relatively stable pore spacing during the
		restrained portion of the dry equilibration procedure
		(Figure~\ref{fig:p2p_45}). We chose to use this value for all our simulations
		in the main text.

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).

		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle once the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps are introduced unnecessarily.

	  \end{enumerate}

	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
  	  \begin{figure}[htp]
		\centering
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_39.png}\quad
			\vspace{-1.25em}
			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_41.png}\quad
			\vspace{-1.25em}
			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_45.png}
			\vspace{-1.25em}
			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
			\vspace{-1.25em}
			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_55.png}
			\vspace{-1.25em}
			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
		\end{subfigure}

		\caption{The pore spacing during the restrained portion of the
			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
			experimental value (a) or at the experimental value (b), there is an abrupt
			change in pore spacing when the position restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA apart (c) the pore spacing
			remains relatively stable. When pores are spaced 50 \AA apart (d), the pore
			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA apart (e), so that monomers
			do not intersect with adjacent pores, and position restraints are reduced to 56
			KJ mol$^{-1}$ nm$^{-2}$, pore spacing changes erratically before stabilizing
			when force constants are reduced to 3 KJ mol$^{-1}$ nm$^{-2}$.} 
		\label{fig:p2p}
	  \end{figure}

	  \item \underline{Initial pore radius}

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~ and the distance between layers constant at
	  3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each frame is calculated as the
	  average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the timeseries
	  representing the average pore radius at each frame.  Equilibration was detected
	  using \texttt{pymbar.timeseries.detectEquilibration}. The average and standard
	  deviation of pore radii were calculated using only data points collected after
	  equilibration was detected.

	  \begin{enumerate}

		\item 2.5 \AA~: The smallest pore radius that we can achieve before energy 
		minimization becomes problematic is 2.5 \AA.

		\item 5 \AA~:

		\item 8 \AA~: The largest pore radius that can achieve before energy minimization
		becomes problematic is 8 \AA.
	  \end{enumerate}

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.394 \pm 0.002$ \AA \\
	  5 \AA   & $0.423 \pm 0.002$ \AA \\ % final result
	  8 \AA   & $0.721 \pm 0.002$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{Caption of the future!}~\label{table:radii}
	  \end{table}

	  \item Initial distance between layers

          We tested 3 different initial layer spacings, defined as the distance between the planes of 
          aromatic rings in each layer. Systems built with layers stacked 3.7 \AA and 5 \AA apart
	  are discussed extensively in the main text. We will focus the discussion here on systems
	  built with layers stacked 10 \AA apart.

  \end{enumerate}
